### 2022-07-12 chapters/optimization/python-dir/python.tex
add : some notes

%%%% python is a popular programming language  based TIOBE PYPI   add graphs

@@

>>>>

@@

\section{placeholder}
we performed a shapiro normality test for the first on the results, and almost all the p-values smaller than alpha=0.01\% 
therefore the distrubution is not normal - which is kinda true because if it was normal then we dont have any comparaison --

for arrays and vectors  graalpython took so much time that we decided to remove it

the startup cost for ironpython was too high 
for graalpython and ipy they couldnt handle big numbers hence the overflow  when it comes to execution time 
but since we measure the energy outside the values of the energy aren't impacted

as usual there is  correlaction between DRAM and CPU so no need to classify based on DRAM + the DRAM consumes less 10\% of the  energy compared to the CPU

so the plan is to prove that there is a statistical difference 
then we use the multiparameter optimization , howerver we stop in the phase where we calculate the score 
because we dont know the weight of each parameter ( of tommti microbenchmark) and instead of doing the sum with the coefissients we use the radar plot to let the reader decide which one is the most suitable for his usage. howerver since the differences are gigantics we change the scale to logarithmic to be easier for the eye to read
